---
title: "R Notebook"
output: html_notebook
---

# Initialize notebook

Load required packages.

```{r load packages, warning=FALSE, message=FALSE}
library( tidyverse )
library( visdat )
library( Hmisc )
library( funModeling ) 
library( brms )
library( tidybayes )
library( bayesplot )
library( googlesheets4 )
library( broom.mixed )
library( psych )
```

Set up workspace, i.e., remove all existing data from working memory, initialize the random number generator, turn of scientific notation of large numbers, set a standard theme for plotting.

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(42)
options(scipen=10000)
```


# Prep data

Load data.

```{r}
df_raw <- read.csv("df.csv") 
glimpse(df_raw)
```

Prepare data 

```{r}

#use raw data to calculate means and transform

#make columns numeric
#only overall rating
df_raw$Only_overall_rating_1 <- as.numeric(df_raw$Only_overall_rating_1)

#story first -- overall rating
df_raw$storyfirst_Overall_1 <- as.numeric(df_raw$storyfirst_Overall_1)

#story last -- overall rating
df_raw$storylast_Overall_1 <- as.numeric(df_raw$storylast_Overall_1)

#make columns numeric
df_raw$Only_overall_rating_1 <- as.numeric(df_raw$Only_overall_rating_1)
df_raw$storyfirst_Overall_1 <- as.numeric(df_raw$storyfirst_Overall_1)
df_raw$storylast_Overall_1 <- as.numeric(df_raw$storylast_Overall_1)


#simple t test
t.test(df_raw$storyfirst_Overall_1, df_raw$storylast_Overall_1)




#now, with filtering (same procecure)
df <- df_raw %>% 
  filter( movie_figures > 30 & movie_figures < 80 ) %>%
  filter(CRT_2_1 == 0.05) %>%
  filter(CRT_3_1 == 47) %>%
  filter(CRT_1_1 == 5)



t.test(df$storyfirst_Overall_1, df$storylast_Overall_1)




#NEW IDEA -- compare storyfirst_1 (story as first dimension) to storylast_4 (story as last dimension, n=746)

t.test(df_raw$storyfirst_1, df_raw$storylast_4)


#now with filtering (even more difference but we loose participants and thus statistical power, n=176)
t.test(df$storyfirst_1, df$storylast_4)






