---
title: "R Notebook"
output: html_notebook
---

# Initialize notebook

Load required packages.

```{r load packages, warning=FALSE, message=FALSE}
library( tidyverse )
library( visdat )
library( Hmisc )
library( funModeling ) 
library( brms )
library( tidybayes )
library( bayesplot )
library( googlesheets4 )
library( broom.mixed )
library( psych )
```

Set up workspace, i.e., remove all existing data from working memory, initialize the random number generator, turn of scientific notation of large numbers, set a standard theme for plotting.

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(42)
options(scipen=10000)
```


# Prep data

Load data.

```{r}
df_raw <- read.csv("Study -- OCR (Bad Framing)_April 8, 2022_06.57.csv") 
glimpse(df_raw)
```

Prepare data 

```{r}
# Select variables

df <- df_raw %>% 
  select( food_first_1:food_first_5, food_last_1:food_last_5, overall.rating._1, story_first_1:story_first_4, story_last_1:story_last_4, movie_overall_1, scenario_timing_Page.Submit, movie_figures, boxes_1, boxes_2, boxes_3 ) %>% 
  rename( Scenario_reading_time = scenario_timing_Page.Submit,
          restaurant_overall_rating = overall.rating._1,
          movie_overall_rating = movie_overall_1 ) %>%
  filter( Scenario_reading_time > 30 ) %>%
  filter( movie_figures > 30 & movie_figures < 80 ) %>%
  filter( boxes_1 > 10 & boxes_1 < 25) %>%
  filter( boxes_2 > 20 & boxes_2 < 35) %>%
  filter( boxes_3 > 55 & boxes_3 < 75)

#implementation of conditions: primacy, recency and overall rating only
df <- df %>% 
mutate( condition = ifelse( !(is.na(food_first_1)), "primacy",                   
                    ifelse( !(is.na(food_last_1)), "recency",
                    ifelse( is.na(food_first_1) & is.na(food_last_1), "overall_rating_only",
                            "NA")))) %>% 
  select( condition, restaurant_overall_rating, movie_overall_rating ) %>%                                                   
  mutate( restaurant_overall_rating = as.integer( restaurant_overall_rating ),
          movie_overall_rating = as.integer( movie_overall_rating ))
  

glimpse( df )
```


# Exploratory data analysis

```{r}
# Restaurant

## Boxplot
df %>%
  ggplot() +
  aes( x = condition, y = restaurant_overall_rating ) +
  geom_boxplot( ) +
  theme_gray() +
  ylab( "Rating")

## Density diagram by condition
df %>% 
  filter( condition != "overall_rating_only" ) %>%
  ggplot(aes( restaurant_overall_rating, fill = condition )) +
  geom_density( alpha = 0.2)

## Histogram by condition
df %>% 
  filter( condition != "overall_rating_only" ) %>%
  ggplot(aes( restaurant_overall_rating, fill = condition )) +
  geom_histogram( position = "dodge" )

## Violin plot by condition
df %>%
ggplot( mapping = aes(y = restaurant_overall_rating, x = condition )) +
  geom_violin() +
  geom_jitter( shape=16, position=position_jitter(0.2), alpha=0.5 ) +
  geom_boxplot( width=0.1, alpha = 0.7 ) + 
  labs(x = "Condition", y="Rating" )


# Movie

## Boxplot
df %>%
  ggplot() +
  aes( x = condition, y = movie_overall_rating ) +
  geom_boxplot( ) +
  theme_gray() +
  ylab( "Rating")

## Density diagram by condition
df %>% 
  filter( condition != "overall_rating_only" ) %>%
  ggplot(aes( movie_overall_rating, fill = condition )) +
  geom_density( alpha = 0.2)

## Histogram by condition
df %>% 
  filter( condition != "overall_rating_only" ) %>%
  ggplot(aes( movie_overall_rating, fill = condition )) +
  geom_histogram( position = "dodge" )

## Violin plot by condition
df %>%
ggplot( mapping = aes(y = movie_overall_rating, x = condition )) +
  geom_violin() +
  geom_jitter( shape=16, position=position_jitter(0.2), alpha=0.5 ) +
  geom_boxplot( width=0.1, alpha = 0.7 ) + 
  labs( x = "Condition", y="Rating" )
```
Descriptive statistics

```{r}
# Restaurant
tapply(df$restaurant_overall_rating, df$condition, summary)

# Movie
tapply(df$movie_overall_rating, df$condition, summary)
```

# Modeling

## Gaussian model

### Restaurant

Prior predictive check

```{r}
m1 <- 
  brm( family = gaussian,                                                                       
       restaurant_overall_rating ~ 0 + condition,                                                           
       prior = c( prior( normal( 5, 0.5 ), class = b ),                      
                  prior( exponential( 1 ), class = sigma )),                                    
       sample_prior = "only",
       data = df,
       iter = 2000, warmup = 1000, chains = 4, cores = 4
     )

# Prior predictive check
pp_check( m1 ) + theme_bw()
```

Add data

```{r}
m1b <- 
  brm( family = gaussian,                                                                       
       restaurant_overall_rating ~ 0 + condition,                                                           
       prior = c( prior( normal( 5, 0.5 ), class = b ),                      
                  prior( exponential( 1 ), class = sigma )),                                    
       # sample_prior = "only",
       data = df,
       iter = 2000, warmup = 1000, chains = 4, cores = 4
     )

# Prior predictive check
pp_check( m1b ) + theme_bw()
```

Plot effects

```{r}
mcmc_areas(
    m1b,
    regex_pars = "b_",
    prob = 0.95,
    point_est = "median",
    area_method = "equal area"
    ) +
    theme_bw()
```

Estimation details

```{r}
tidy( m1b )
```

Hypotheses tests

```{r}
# RQ1: Do ratings differ between conditions?
hyp1 <- hypothesis( m1b, "conditionprimacy > conditionrecency", alpha = 0.05 )
plot( hyp1 )
hyp1
```

### Movie

Prior predictive check

```{r}
m2 <- 
  brm( family = gaussian,                                                                       
       movie_overall_rating ~ 0 + condition,                                                           
       prior = c( prior( normal( 5, 0.5 ), class = b ),                      
                  prior( exponential( 1 ), class = sigma )),                                    
       sample_prior = "only",
       data = df,
       iter = 2000, warmup = 1000, chains = 4, cores = 4
     )

# Prior predictive check
pp_check( m2 ) + theme_bw()
```

Add data

```{r}
m2b <- 
  brm( family = gaussian,                                                                       
       movie_overall_rating ~ 0 + condition,                                                           
       prior = c( prior( normal( 5, 0.5 ), class = b ),                      
                  prior( exponential( 1 ), class = sigma )),                                    
       # sample_prior = "only",
       data = df,
       iter = 2000, warmup = 1000, chains = 4, cores = 4
     )

# Prior predictive check
pp_check( m2b ) + theme_bw()
```

Plot effects

```{r}
mcmc_areas(
    m2b,
    regex_pars = "b_",
    prob = 0.95,
    point_est = "median",
    area_method = "equal area"
    ) +
    theme_bw()
```

Estimation details

```{r}
tidy( m2b )
```

Hypotheses tests

```{r}
# RQ1: Do ratings differ between conditions?
hyp1 <- hypothesis( m2b, "conditionprimacy > conditionrecency", alpha = 0.05 )
plot( hyp1 )
hyp1
```

## Ordinal model

### Restaurant

Prior predictive check

```{r}
m3 <- brm( family = cumulative,
           formula = restaurant_overall_rating ~ condition,
           prior = c(prior(normal(0, 1.5), class = Intercept),
           prior(normal(0, 0.5), class = b)),
           sample_prior = "only",
           data = df, 
           iter = 2000, warmup = 1000, cores = 4, chains = 4 )

# Prior predictive check
pp_check( m3 ) + theme_bw()
```

Add data

```{r}
m3b <- brm( family = cumulative,
            formula = restaurant_overall_rating ~ condition,
            prior = c(prior(normal(0, 1.5), class = Intercept), 
                      prior(normal(0, 0.5), class = b)),
            # sample_prior = "only",
            data = df, 
            iter = 2000, warmup = 1000, cores = 4, chains = 4 )

# Prior predictive check
pp_check( m3b ) + theme_bw()
```

Compare models

```{r}
m1b <- add_criterion( m1b, c( "loo", "waic" ))   # Gaussian model
m3b <- add_criterion( m3b, c( "loo", "waic" ))  # ordinal model

loo_compare( m1b, m3b, criterion = "loo" ) %>% print( simplify = F )
```

Plot effects

```{r}
mcmc_areas(
    m3b,
    pars = c( "b_conditionprimacy", "b_conditionrecency"),
    #regex_pars = "b_",
    prob = 0.95,
    point_est = "median",
    area_method = "equal area"
    ) +
    theme_bw()
```

Estimation details

```{r}
tidy( m3b )
```

Hypotheses

```{r}
# RQ1: Is intercept larger than 50% (log-odd = 0)
q1 <- hypothesis( m3b, "conditionprimacy > conditionrecency" )
q1
plot(q1)
```

### Movie

Prior predictive check

```{r}
m4 <- brm( family = cumulative,
           formula = movie_overall_rating ~ condition,
           prior = c(prior(normal(0, 1.5), class = Intercept),
           prior(normal(0, 0.5), class = b)),
           sample_prior = "only",
           data = df, 
           iter = 2000, warmup = 1000, cores = 4, chains = 4 )

# Prior predictive check
pp_check( m4 ) + theme_bw()
```

Add data

```{r}
m4b <- brm( family = cumulative,
            formula = movie_overall_rating ~ condition,
            prior = c(prior(normal(0, 1.5), class = Intercept), 
                      prior(normal(0, 0.5), class = b)),
            # sample_prior = "only",
            data = df, 
            iter = 2000, warmup = 1000, cores = 4, chains = 4 )

# Prior predictive check
pp_check( m4b ) + theme_bw()
```

Compare models

```{r}
m2b <- add_criterion( m2b, c( "loo", "waic" ))   # Gaussian model
m4b <- add_criterion( m4b, c( "loo", "waic" ))  # ordinal model

loo_compare( m2b, m4b, criterion = "loo" ) %>% print( simplify = F )
```

Plot effects

```{r}
mcmc_areas(
    m4b,
    pars = c( "b_conditionprimacy", "b_conditionrecency"),
    # regex_pars = "b_",
    prob = 0.95,
    point_est = "median",
    area_method = "equal area"
    ) +
    theme_bw()
```

Estimation details

```{r}
tidy( m4b )
```

Hypotheses

```{r}
# RQ1: Is intercept larger than 50% (log-odd = 0)
q1 <- hypothesis( m4b, "conditionprimacy > conditionrecency" )
q1
plot(q1)
```


