---
title: "R Notebook"
output: html_notebook
---

# Initialize notebook

Load required packages.

```{r load packages, warning=FALSE, message=FALSE}
library( tidyverse )
library( visdat )
library( Hmisc )
library( funModeling ) 
library( brms )
library( tidybayes )
library( bayesplot )
library( googlesheets4 )
library( broom.mixed )
library( psych )
library( stargazer )
```

Set up workspace, i.e., remove all existing data from working memory, initialize the random number generator, turn of scientific notation of large numbers, set a standard theme for plotting.

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(42)
options(scipen=10000)
```


# Prep data

Load data.

```{r}
df_raw <- read.csv("Primacy_Recency_pilot3.csv") 
glimpse(df_raw)
```

Prepare data 

```{r}
# Select variables

df <- df_raw %>% 
  select( storyfirst_1:storyfirst_4, storylast_1:storylast_4, storyfirst_Overall_1, storylast_Overall_1, Only_overall_rating_1, movie_figures ) %>% 
  rename( storyfirst_Overall = storyfirst_Overall_1,
          storylast_Overall = storylast_Overall_1,
          no_story_Overall = Only_overall_rating_1 ) %>%
  filter( movie_figures > 30 & movie_figures < 80 ) 

#implementation of conditions: primacy, recency and overall rating only
df <- df %>% 
  mutate( condition = ifelse( !(is.na(storyfirst_1)), "primacy",                   
                    ifelse( !(is.na(storylast_1)), "recency",
                    ifelse( is.na(storyfirst_1) & is.na(storylast_1), "overall_rating_only",
                            "NA")))) %>%
  unite( movie_overall_rating, c( storyfirst_Overall, storylast_Overall, no_story_Overall ),      # create movie overall_rating variable
         na.rm = T ) %>%
  unite( story_1, c( storyfirst_1, storylast_1 ),      # create first story dimension
         na.rm = T ) %>%
  unite( story_2, c( storyfirst_2, storylast_2 ),      # create second story dimension
         na.rm = T ) %>%
  unite( story_3, c( storyfirst_3, storylast_3 ),      # create third story dimension
         na.rm = T ) %>%
  unite( story_4, c( storyfirst_4, storylast_4 ),      # create fourth story dimension
         na.rm = T ) %>% 
  select( condition, movie_overall_rating, story_1, story_2, story_3, story_4 ) %>%                                                   
  mutate( movie_overall_rating = as.integer( movie_overall_rating ),
          story_1 = as.integer( story_1 ),
          story_2 = as.integer( story_2 ),
          story_3 = as.integer( story_3 ),
          story_4 = as.integer( story_4 )) 

%>%
  filter( condition != "overall_rating_only") # drop overall-rating-only condition
  

glimpse( df )
```


# Exploratory data analysis

```{r}
basic_eda <- function(data)
{
  glimpse(data)
  print(status(data))
  freq(data) 
  print(profiling_num(data))
  plot_num(data)
  #describe(data)
}

basic_eda( df )
```

```{r}
## Boxplot
df %>%
  ggplot() +
  aes( x = condition, y = movie_overall_rating ) +
  geom_boxplot( ) +
  theme_gray() +
  ylab( "Rating")

## Density diagram by condition
df %>% 
  # filter( condition != "overall_rating_only" ) %>%
  ggplot(aes( movie_overall_rating, fill = condition )) +
  geom_density( alpha = 0.2)

## Histogram by condition
df %>% 
  # filter( condition != "overall_rating_only" ) %>%
  ggplot(aes( movie_overall_rating, fill = condition )) +
  geom_histogram( position = "dodge" )

## Violin plot by condition
df %>%
  # filter( condition != "overall_rating_only" ) %>%
  ggplot( mapping = aes(y = movie_overall_rating, x = condition )) +
  geom_violin() +
  geom_jitter( shape=16, position=position_jitter(0.2), alpha=0.5 ) +
  geom_boxplot( width=0.1, alpha = 0.7 ) + 
  labs( x = "Condition", y="Rating" )
```
Descriptive statistics

```{r}
describeBy(df$movie_overall_rating, df$condition)

tapply(df$movie_overall_rating, df$condition, summary)
```

# t-test

```{r}
t.test( df$movie_overall_rating ~ df$condition, var.equal = T, alternative = "two.sided" )
```


# Simple linear regression

```{r}
fit <- lm( movie_overall_rating ~ condition, data = df)
stargazer( fit, type = "text" )
```






# Modeling Bayes

## Gaussian model

Prior predictive check

```{r}
m2 <- 
  brm( family = gaussian,                                                                       
       movie_overall_rating ~ 0 + condition,                                                           
       prior = c( prior( normal( 5, 0.5 ), class = b ),                      
                  prior( exponential( 1 ), class = sigma )),                                    
       sample_prior = "only",
       data = df,
       iter = 2000, warmup = 1000, chains = 4, cores = 4
     )

# Prior predictive check
pp_check( m2 ) + theme_bw()
```

Add data

```{r}
m2b <- 
  brm( family = gaussian,                                                                       
       movie_overall_rating ~ 0 + condition,                                                           
       prior = c( prior( normal( 5, 0.5 ), class = b ),                      
                  prior( exponential( 1 ), class = sigma )),                                    
       # sample_prior = "only",
       data = df,
       iter = 2000, warmup = 1000, chains = 4, cores = 4
     )

# Prior predictive check
pp_check( m2b ) + theme_bw()
```

Plot effects

```{r}
mcmc_areas(
    m2b,
    regex_pars = "b_",
    prob = 0.95,
    point_est = "median",
    area_method = "equal area"
    ) +
    theme_bw()
```

Estimation details

```{r}
tidy( m2b )
```

Hypotheses tests

```{r}
# RQ1: Do ratings differ between conditions?
hyp1 <- hypothesis( m2b, "conditionprimacy > conditionrecency", alpha = 0.05 )
plot( hyp1 )
hyp1
```

## Ordinal model

Prior predictive check

```{r}
m4 <- brm( family = cumulative,
           formula = movie_overall_rating ~ condition,
           prior = c(prior(normal(0, 1.5), class = Intercept),
           prior(normal(0, 0.5), class = b)),
           sample_prior = "only",
           data = df, 
           iter = 2000, warmup = 1000, cores = 4, chains = 4 )

# Prior predictive check
pp_check( m4 ) + theme_bw()
```

Add data

```{r}
m4b <- brm( family = cumulative,
            formula = movie_overall_rating ~ condition,
            prior = c(prior(normal(0, 1.5), class = Intercept), 
                      prior(normal(0, 0.5), class = b)),
            # sample_prior = "only",
            data = df, 
            iter = 2000, warmup = 1000, cores = 4, chains = 4 )

# Prior predictive check
pp_check( m4b ) + theme_bw()
```

Compare models

```{r}
m2b <- add_criterion( m2b, c( "loo", "waic" ))   # Gaussian model
m4b <- add_criterion( m4b, c( "loo", "waic" ))  # ordinal model

loo_compare( m2b, m4b, criterion = "loo" ) %>% print( simplify = F )
```

Plot effects

```{r}
mcmc_areas(
    m4b,
    pars = c( "b_conditionprimacy", "b_conditionrecency"),
    # regex_pars = "b_",
    prob = 0.95,
    point_est = "median",
    area_method = "equal area"
    ) +
    theme_bw()
```

Estimation details

```{r}
tidy( m4b )
```

Hypotheses

```{r}
# RQ1: Is intercept larger than 50% (log-odd = 0)
q1 <- hypothesis( m4b, "conditionprimacy > conditionrecency" )
q1
plot(q1)
```


